Software Product Line Analysis Techniques

### 2018-03-05 doc/quals/quals.tex
moving table to intro

This report covers some research work attempting to solve this problem. One paper compares brute force (product-based), variability-aware (family-based) and sampling techniques~\cite{Apel:2013}. Another extends this work to more elaborate sampling techniques and more general categories of analysis~\cite{Liebig:2013}. At the theoretical end of the spectrum, one paper provides an elaborate mathematical foundation for lifting abstract interpretation based analyses to SPLs~\cite{Midtgaard:2015}. At the other end, some papers provide pragmatic implementations of type checkers~\cite{Kastner:2012}, source code syntax checkers~\cite{Gazzillo:2012}, data flow analyses~\cite{Bodden:2013}, and model checkers~\cite{Classen:2013}.

@@

\begin{table}[h!]
\begin{tabular}{ |l|l|l|l|}
\hline
Paper & Analysis & Limitation \\
\hline
Apel et al.~\cite{Apel:2013} & Model Checking & Generative SPLs only  \\
Liebig et al.~\cite{Liebig:2013} & Static Analysis & Hand-crafted analyses and infrastructure  \\
Midtgaard et al.~\cite{Midtgaard:2015} & Abstract Interpretation & Systematic but not automated \\
K\"{a}stner et a.~\cite{Kastner:2012} & Type Checking & Limited source code variability \\
Gazzillo and Grimm~\cite{Gazzillo:2012} & Parsing (Syntax Checking) & Fully hand-crafted \\
Bodden et al.~\cite{Bodden:2013} & Data-flow Analysis & IFDS analyses only \\
Classen et al.~\cite{Classen:2013} & Model Checking & Hand-crafted \\
\hline
\end{tabular}
\caption{Different SPL analysis techniques covered in this report.}
\label{tbl1}
\end{table}

Family-based analysis of SPLs covers all valid product line instances, and in many cases outperforms sampling techniques~\cite{Apel:2013, Liebig:2013}. Different family-based analysis techniques have been covered in this report. Table \ref{tbl1} summarizes the papers covered.

Late splitting and early joining are two principles that underly many of the techniques presented. These two principles maximize reuse of intermediate results calculated as a part of the analysis process. Local variability representation is another principle that manages intermediate value variability. These principles together with some analysis specific design decisions can effectively lead to an efficient family-based analysis.
\bibliographystyle{abbrv}
\bibliography{quals} 
\end{document}

>>>>

This report covers some research work attempting to solve this problem. One paper compares brute force (product-based), variability-aware (family-based) and sampling techniques~\cite{Apel:2013}. Another extends this work to more elaborate sampling techniques and more general categories of analysis~\cite{Liebig:2013}. At the theoretical end of the spectrum, one paper provides an elaborate mathematical foundation for lifting abstract interpretation based analyses to SPLs~\cite{Midtgaard:2015}. At the other end, some papers provide pragmatic implementations of type checkers~\cite{Kastner:2012}, source code syntax checkers~\cite{Gazzillo:2012}, data flow analyses~\cite{Bodden:2013}, and model checkers~\cite{Classen:2013}. Table \ref{tbl1} summarizes the papers covered, with limitations explained throughout this report.

\begin{table}[h!]
\begin{tabular}{ |l|l|l|l|}
\hline
Paper & Analysis & Limitations \\
\hline
Apel et al.~\cite{Apel:2013} & Model Checking & Generative SPLs only  \\
Liebig et al.~\cite{Liebig:2013} & Static Analysis & Hand-crafted analyses and infrastructure  \\
Midtgaard et al.~\cite{Midtgaard:2015} & Abstract Interpretation & Systematic but not automated \\
K\"{a}stner et a.~\cite{Kastner:2012} & Type Checking & Limited source code variability \\
Gazzillo and Grimm~\cite{Gazzillo:2012} & Parsing (Syntax Checking) & Fully hand-crafted \\
Bodden et al.~\cite{Bodden:2013} & Data-flow Analysis & IFDS analyses only \\
Classen et al.~\cite{Classen:2013} & Model Checking & Hand-crafted \\
\hline
\end{tabular}
\caption{Different SPL analysis techniques covered in this report.}
\label{tbl1}
\end{table}

@@

Family-based analysis of SPLs covers all valid product line instances, and in many cases outperforms sampling techniques~\cite{Apel:2013, Liebig:2013}. Different family-based analysis techniques have been covered in this report.

Late splitting and early joining are two principles that underly many of the techniques presented. These two principles maximize reuse of intermediate results calculated as a part of the analysis process. Local variability representation is another principle that manages intermediate value variability. These principles together with some analysis-specific design decisions can effectively lead to an efficient family-based analysis.
\bibliographystyle{abbrv}
\bibliography{quals} 
\end{document}
